What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-12-11 Manuscript files/Manuscript.qmd
Conclusion

>>>>

Complementing the analyses reported in @rudolph_citizens_2024, we used the novel cjbart approach by @robinson_how_2024 to scrutinize the present conjoint data for effect heterogeneity.
Specifically, we found that the importance of certain attributes (levels) differed with regard to country, where differences were most pronounced for the distinction UK vs. the other four countries.
For example, for all five countries selection probabilities decreased with increasing civilian casualties but the effect was stronger for non-UK participants.
Similarly, the opinion that Ukraine should not make any concessions to Russia to end the aggression predicted some heterogeneity.
People who oppose concessions favored profiles that were associated with higher numbers of killed Russian soldiers, while for concession proponents the selection probability decreased.

With AMCE estimates similar to the primary analysis reported by @rudolph_citizens_2024, we believe that the newly developed cjbart-method provides a powerful tool to investigate effect heterogeneity in high-dimensional conjoint data.
As with any new method, further methodological research is needed to assess to capabilities of the method under different conditions.
Most importantly, the results of cjbart should always be interpreted as what they are: an exploratory peek into underlying causal relations between covariates and individual preferences for certain attributes (i.e., IMCEs).
Our recommendation is to use these exploratory insights to generate hypotheses that can subsequently be tested to inform political theory.
